Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-11 write-ups/PLDI/paper.tex
Fixed missing refs.

In Section~\ref{sec:cooperativeexamples} we show how the work stealing
and graph traversal examples of Figures~\ref{fig:workstealing} and~\ref{fig:graphsearch} can be
updated to use our cooperative kernels programming model to resolve
the scheduling issue.

@@

\myfiglong\ref{fig:workstealing-cooperative} shows a cooperative
version of the work stealing example of \myfig\ref{...} that we
discussed in \mysec\ref{sec:openclexamples}.
\ADComment{TODO: go through with Hugues; where are the offer functions?}

@@

\caption{Cooperative version of the work stealing example from \myfig\ref{fig:XXX}; the number of workpools
must be explicitly passed as arguments since the number of workgroups
is not a constant anymore}\label{fig:workstealing-cooperative}
\end{figure}

@@

In \mysec\ref{ } we describe the set of irregular GPU algorithms used
in our experiments, which largely captures the irregular blocking
algorithms that are available as open source GPU kernels.  These all
employ either work stealing or operate on graph data structures.
Like the simplified example of \myfig\ref{ }, the work stealing algorithms have a transactional flavour
and require little or no state to be carried between transactions.  Thus the point at which a workgroup is ready to process a new task is a natural point to place $\offerkill$ and $\offerfork$, and few or no $\transmit$ annotations are required.
%
The example of \myfig\ref{fig:cgraphsearch} is simpler than, but representative of,
most level-by-level graph algorithms.  These algorithms tend to
require more state to be annotated with $\transmit$, and in some cases
a global barrier is required in the midst of a transaction, in which
case $\globalbarrier$, but not $\resizingglobalbarrier$, is suitable
for achieving synchronization without disturbing the set of active
workgroups.  But often it is the case that on completing a level of
the graph algorithm, the next level could be processed by more or
fewer workgroups, something which $\resizingglobalbarrier$
facilitates.

>>>>

In Section~\ref{sec:programmingguidelines} we show how the work stealing
and graph traversal examples of Figures~\ref{fig:workstealing} and~\ref{fig:graphsearch} can be
updated to use our cooperative kernels programming model to resolve
the scheduling issue.

@@

\myfiglong\ref{fig:workstealing-cooperative} shows a cooperative
version of the work stealing example of \myfig\ref{fig:workstealing} that we
discussed in \mysec\ref{sec:openclexamples}.
\ADComment{TODO: go through with Hugues; where are the offer functions?}

@@

\caption{Cooperative version of the work stealing example from \myfig\ref{fig:workstealing}; the number of workpools
must be explicitly passed as arguments since the number of workgroups
is not a constant anymore}\label{fig:workstealing-cooperative}
\end{figure}

@@

In \mysec\ref{sec:portingalgorithms} we describe the set of irregular GPU algorithms used
in our experiments, which largely captures the irregular blocking
algorithms that are available as open source GPU kernels.  These all
employ either work stealing or operate on graph data structures.
Like the simplified example of \myfig\ref{fig:workstealing-cooperative}, the work stealing algorithms have a transactional flavour
and require little or no state to be carried between transactions.  Thus the point at which a workgroup is ready to process a new task is a natural point to place $\offerkill$ and $\offerfork$, and few or no $\transmit$ annotations are required.
%
The example of \myfig\ref{fig:cgraphsearch} is simpler than, but representative of,
most level-by-level graph algorithms.  These algorithms tend to
require more state to be annotated with $\transmit$, and in some cases
a global barrier is required in the midst of a transaction, in which
case $\globalbarrier$, but not $\resizingglobalbarrier$, is suitable
for achieving synchronization without disturbing the set of active
workgroups.  But often it is the case that on completing a level of
the graph algorithm, the next level could be processed by more or
fewer workgroups, something which $\resizingglobalbarrier$
facilitates.
